In my honest opinion I believe the project went very well in regards to how the team was able to micro-manage itself and collaborate to this end to produce a solid piece of work. Although it was a rough start with establishing how the project was run and for groups to learn to manage themselves, this was effectively addressed as the meetings with Judy, in regards to reviewing the prototypes, established a consensus of what the next week's deliverable would consist of and who would be responsible for what. It was unfortunate that one week we missed a deadline but I'm happy that management had inserted contingency weeks in the time line as they proved invaluable and allowed us to make up for the mistake. On another note, I was disappointed that we were unable to use the Kinect to a higher extent but after speaking with the teams involved it seems that it could have proved to be more work than gain and appreciate that the team worked to this end.

I particularly liked how the project worked from a client's specification rather then gathering and evaluating user-based requirements as I believe it allowed for the team to be more experimental and obtain both a paper and electronic prototype within the first few weeks to good effect. This allowed for the team to again split the work up effectively and micromanage itself whilst preparing a new implementation each week from which the client could assess it and offer their feedback. I believe this approach, and methodology, was essential to the team producing a strongly tested, and evaluated, piece of work on time for submission.

Although I am happy that the final product is ready for its initial purpose, I would hope that another group could take it upon themselves to work towards developing the application further in regards to the game aspect as I believe this would best utilize the application's strengths. Ideally combining the current application with even a basic game would allow the application to target a wider audience.

In the end, I'm very happy with the design and final application and appreciate how the project allowed for all members to return from their work placements and work together a final time towards something worth while.
