I think the overall project is a success. Although the group knew each
other from the previous years, it was the really first time everyone had
the chance to work with each other, and yet everyone managed to work as a
team. 

As soon as the project was defined each of us talked on who would be
affected to which task, this part of the management could have been a
lot of pain for all of us, as it is usual among programmers that everyone
want to work on one "programming" part of the project. It was not the
case at all, and the work splitting has been really trivial, as the
groups formed them self by skills and needs. This allowed the group
to quickly put a prototype together.

Moreover, the team availability was really high. Even though it happened
that people missed meeting the overall attendance was really good and
more than I would normally expect. A good example for that is the users
testing week, at which everyone attended and stayed more time than
agreed, which is good. The communication in between the small teams was
good, it lacked at some point resulting in a missed prototype cycle
on week 4. But the team learned out of this mistakes and the prototype
got back on schedule in less than a week reaching the features
implementation needed in week 5, in week 5.

I worked with Pierre-André on the server. Pierre-André had more experiences
and skills than me using C# and though I learned a lot with him.
Although I managed to design the server in terms of architecture and to
program a good part of the server along with Pierre-André. I'm really
satisfied with the work we have accomplished on the server. The server
coding and design are easy to read and understand, it allow future works
to be integrated in a smooth way.

I also worked closely with Chris and Alex as the server needs data fetched
from the web server (News feed). This collaboration went really well and
the work and needed modification happened in a nice and smooth process.

I really enjoyed the users testing week, as it was a nice and rewarding 
part of the project in which we have been able to see people playing with
the software we have been working on for weeks. It was nice to have feedbacks
on the existing feature, and new ideas on what could be added. Most of the
new ideas are present in this report as part of the possible improvments that
could be done in future work.

Finaly, the project have been fun, and I'm glad to have been a part of it.
I enjoyed working with the other MEng students and learned a lot from them,
and been able to share my experiences and knowledge as well. I would deffinitly
come back next year to hopefully see our work displayed in the cursh area.